\section{Introduction}
\label{sec:introduction}

Mobility is an essential piece of our life.
In recent years, transportation systems and automobiles are becoming
more and more intelligent underlying high-efficient mobility of the
societal infrastructure.
Such innovations in mobility could reduce car accidents, remove human\'s
stress, improve traffic throughput, and create new markets.
Towards this end, the next-generation mobility infrastructure is expected to 
achieve a tight coordination of computer systems and physical elements,
often referred to as cyber-physical systems (CPS), facilitating a
cyber-understanding of the physical world.
A core challenge to this mobility CPS, however, is a power and space
constraint of each mobility component.
For example, moving vehicles cannot accommodate rich computer systems
due to the limited battery power.
Particularly the computational cost with respect to a
cyber-understanding of the physical world is very high and the computing
capability of current vehicular embedded systems is woefully
inadequate.
In order to address this trade-off, mobility CPS must seek for a
cooperation with advanced information and communication
technology (ICT) such as cloud computing and smart devices.

A good example of computationally-expensive mobility CPS applications is
an autonomous vehicle~\cite{Guizzo11, Levinson11, Urmson08}, which is
required to recognize roads, traffic signs, surrounding vehicles, and
pedestrians in real-time.
An autonomous vehicle in the current state of the art tends to use laser
sensors and/or cameras for those environmental perception tasks.
The laser sensors can detect object edges as a set of 3-D points by
hardware, reducing the computational requirement imposed on the
vehicular system software, but are generally very expensive way beyond
consumer electronics prices.
On the other hand, the cameras are less expensive in price but come
available in exchange with computational cost, because image processing
is highly compute-intensive.
It would require a rich set of multicore CPUs and hardware accelerators
such as GPUs to meet the desired frame rate.
Unfortunately these devices may not be affordable for battery-operated
vehicular systems due to power consumption issues.
As aforementioned, therefore, we should seek for a possibility of
employing cloud computing technology to offload compute-intensive tasks
onto high-performance computing (HPC) servers over the network.
A question raised herein is ``what is the overhead of offloading
computation and associated data to the cloud?''
If this overhead is acceptable, commodity ICT platforms will be a strong
basis for mobility CPS applications.

\textbf{Contribution:}
We present a prototype implementation of commodity ICT platforms for
mobility CPS applications to quantify the overhead of offloading
computation and data to the cloud.
Specifically we focus on an autonomous vehicle as an example of
mobility CPS applications, and leverage a commodity smartphone and
PC server to process images and control the autonomous vehicle.
The overhead of transferring images over the network governs the frame
rate of image processing in the cloud while that of transferring control
commands determines the minimum feedback-control period of autonomous
driving.
We demonstrate that the bottleneck of networked image processing can be
found in the computation time itself rather than the network
communication overhead.
We also find that the network throughput of commodity ICT is sufficient
to execute autonomic control but the worst-case latency must be bounded
to provide stability.
Our contribution is a useful insight into a coordination of commodity
ICT and mobility CPS.

\textbf{Organization:}
The rest of this paper is organized as follows.
Section \ref{sec:concept} describes the basic concept behind this
paper.
Section \ref{sec:prototype} presents our prototyping of ICT platforms
for an autonomous vehicle as an example of mobility CPS applications.
Section \ref{sec:evaluation} provides the evaluation of overhead imposed
on data transfers over the network relevant to remote vehicle control
and networked image processing.
This paper concludes in Section \ref{sec:conclusion}.